relauo Amicus Brief Models

### 2022-05-15 modeling/amicus_type/relauo.Rmd
rm nonftyp

---
title: "Relauo Amicus Brief Models"
author: "Amanda Konet"
date: "`r Sys.Date()`"
output: pdf_document
---

@@

```{r}
data <- box_read(final_cases) %>% 
  filter(justicevot != "NA") %>% 
  mutate(justicevot = as.numeric(justicevot),
         justiceid = as.factor(justiceid),
         justicefem = as.factor(justicefem),
         nonftyp2 = as.factor(nonftyp2),
         lcdisdirfem = ifelse(lcdisdirfem==1, 0, 1),
         lcdisdirfem = as.factor(lcdisdirfem),
         cirsplit = as.factor(cirsplit)) %>% 
  mutate(across(c(relauo_abortion_different:relauo_womens_rights), ~replace_na(.x, 0)))
```

Add Case ID-- this will be the second level var

```{r}
case_ids <- data %>% distinct(case) %>% arrange(case) %>% mutate(id = 1:n())
data <- case_ids %>% left_join(., data, by = "case")
#data %>% head(1) %>% select(case:justicefem)
```

@@

```{r}
data <- data %>%
  select(case:cirsplit, poppam, relauo_abortion_different:relauo_womens_rights) %>% 
  mutate(across(c(where(is.numeric), -justicevot, -id, -cirsplit),
                ~(scale(., center=T, scale=T))))
                #~(scale(., center=T, scale=T) %>% as.vector)))

total_cols <- data %>% select(contains('relauo')) %>% colnames()
data <- janitor::remove_empty(data, which = "cols")
remaining_cols <- data %>% select(contains('relauo')) %>% colnames()
setdiff(total_cols, remaining_cols)
```

@@

* 0: 
* 0.01:
* 0.05: abortion regret
* 0.10: evidence
* 0.20: bad law, compulsory motherhood, women's health

# Abortion different

```{r}
mod1 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauo_abortion_different + poppam,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod1,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

summary(mod1)
```

@@

```{r}
mod3 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauo_abortion_regret + poppam,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod4 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauo_bad_law + poppam,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

# Comp Motherhood

```{r}
mod6a <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauo_compulsory_motherhood + poppam,
              family = binomial, data = data,  
              nAGQ = 1, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod6a,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

summary(mod6a)
```

# Compulsory Motherhood II

```{r}
mod6b <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauo_compulsory_motherhood_ii + poppam,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod6b,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

summary(mod6b)
```

@@

```{r}
mod9 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauo_evidence + poppam,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

@@

```{r}
mod12 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauo_final_authority + poppam,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod14 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauo_morality_religion + poppam,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod15 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauo_overturn_roe + poppam,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod18 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauo_privacy + poppam,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod20 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauo_standing + poppam,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod22 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauo_uncertainty + poppam,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod23 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauo_undue_burden + poppam,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod24 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauo_untruthful + poppam,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod25 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauo_womens_future_life + poppam,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod26 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauo_womens_health + poppam,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod27 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                relauo_womens_rights + poppam,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

>>>>

---
title: "relauo Amicus Brief Models"
author: "Amanda Konet"
date: "`r Sys.Date()`"
output: pdf_document
---

@@

```{r}
data <- box_read(final_cases) %>% 
  filter(justicevot != "NA") %>% 
  mutate(justicevot = as.numeric(justicevot),
         justiceid = as.factor(justiceid),
         justicefem = as.factor(justicefem),
         nonftyp2 = as.factor(nonftyp2),
         lcdisdirfem = ifelse(lcdisdirfem==1, 0, 1),
         lcdisdirfem = as.factor(lcdisdirfem),
         #sgfem3 = as.factor(sgfem3), 
         cirsplit = as.factor(cirsplit)) %>% 
  mutate(across(c(relauo_abortion_different:relauo_womens_rights), ~replace_na(.x, 0))) %>% 
  filter(case != "Gonzales v PP")

# add case ID (second level var)
case_ids <- data %>% distinct(case) %>% arrange(case) %>% mutate(id = 1:n())
data <- case_ids %>% left_join(., data, by = "case")
```

@@

```{r}
data <- data %>%
  select(case:cirsplit, poppam, relauo_abortion_different:relauo_womens_rights) %>%  
  mutate(across(c(where(is.numeric), -justicevot, -id, -cirsplit, -sgfem3),
                ~(scale(., center=T, scale=T))))
                #~(scale(., center=T, scale=T) %>% as.vector)))

total_cols <- data %>% select(contains('relauo')) %>% colnames()
data <- janitor::remove_empty(data, which = "cols")
remaining_cols <- data %>% select(contains('relauo')) %>% colnames()
#setdiff(total_cols, remaining_cols)
```

@@

* 0:
* 0.01:
* 0.05: abortion regret (+)
* 0.10: evidence (+)
* 0.20: bad law (+), women's health (+)

@@

```{r}
mod3 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam +
                relauo_abortion_regret,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod4 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                relauo_bad_law,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

@@

```{r}
mod9 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                relauo_evidence,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

# Fetus

```{r}
mod11 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                relauo_fetus,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod11,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

summary(mod11)
```

@@

```{r}
mod12 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam +
                relauo_final_authority,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod14 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                relauo_morality_religion,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod15 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam +
                relauo_overturn_roe,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod18 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                relauo_privacy,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod20 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam +
                relauo_standing,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod22 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                relauo_uncertainty,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod23 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                relauo_undue_burden,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod24 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                relauo_untruthful,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod25 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam +
                relauo_womens_future_life,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod26 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                relauo_womens_health,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod27 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                relauo_womens_rights,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
